---
title: "JIRA Export"
author: "Lars Vilhuber"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: 
    keep_md: yes
---


AEA uses JIRA to track verification requests. The files have been anonymized, as they contain individual names. The anonymized data, and the programs to generate them, can be found in 

> Vilhuber,  Lars. 2023.  "Process  data  for  the AEA  Pre-publication  Verification  Service." American Economic Association [publisher], https://doi.org/10.3886/E117876V2

## Local copy

```{r setup,include=FALSE}
### Load libraries 
### Requirements: have library *here*
source(here::here("global-libraries.R"),echo=TRUE)
source(here::here("programs","config.R"),echo=TRUE)
```

A copy has been provided here for convenience. It was downloaded from [`r jira.anon.urlbase`](`r jira.anon.urlbase`).

## Checksums

```{r verify_data}
# Read in data extracted from Jira, anonymized

message("Attempting to download file")
try(download.file(jira.anon.url,paste0(jira.anon.name,"2"),mode="wb"))
if ( file.exists(jira.anon.name) ) {
    message("Download successful, proceeding.")
} else {
    stop("Download failed. Please investigate")
}

# Compute digests for remote and local file
jira.anon.remote <- readRDS(paste0(jira.anon.name,"2"))
jira.anon <- readRDS(jira.anon.name) 
#
# This should be compared to the published version.
#
jira.test.chksum <- digest(jira.anon,algo="sha256")

if ( jira.test.chksum == jira.anon.sha256) {
  message("SHA256 checksum verified.")
} else {
  stop("SHA256 fails, please verify that you are using the same file. Update config.R if necessary.")
}

# report it all
chksum.table <- tibble(Note = "Checksum on file", SHA256 = jira.anon.sha256)
chksum.table <- bind_rows(chksum.table,
                         tibble(Note = "Remote source file", SHA256 = digest(jira.anon.remote,algo="sha256")),
                         tibble(Note = "Local copy", SHA256 = jira.test.chksum)
)
                         
```

The following are the checksums associated with these files:

```{r table,echo=FALSE}
knitr::kable(chksum.table)
```


