---
title: "AEA Annual Report Yearly"
author: "Stuti Goyal"
date: "2023-11-22"
output: html_document
---

```{r}
library(tidyverse)
library(janitor)
library(dataverse)
library(ggplot2)
library(qdapRegex)
library(here)
library(digest)

# dynamically set directory
basedir <- here::here()

# configure some placeholders

dv.fileid <- 8149625
dv.doi    <- "DVN/8YNXVW"

# directories 

outputs  <- file.path(basedir,"Output")
data     <- file.path(basedir,"Data")


for ( dir in list(outputs,data)){
  if (file.exists(dir)){
  } else {
    dir.create(file.path(dir))
  }
}

# convenience functions outsourced...

source(file.path(basedir,"Scripts","00_functions.R"))

# For graphing

evenbreaks = c(2014, 2016, 2018, 2020, 2022)
oddbreaks = c(2013, 2015, 2017, 2019, 2021, 2023)


# file names

rct.file.local <- file.path(data,"trials.Rds")
rct.file.chk256 <- "d7f5f31080f3d4b6dc0c347ad9be9f5c2a508c3178c469259f2abc35ec168985"

```

```{r, message=TRUE}

if ( file.exists(rct.file.local)) {
  message(paste0("Using local file ",rct.file.local))
  aea_orig <- readRDS(file=rct.file.local)

} else {
   aea_orig <- get_dataframe_by_id(file = dv.fileid,
                             server = "dataverse.harvard.edu",
                             .f = read.csv, original = T )
   saveRDS(aea_orig,file=rct.file.local)
}

rct.test.chksum <- digest(rct.file.local,algo="sha256")
message(paste0("SHA256: ",rct.test.chksum))
if ( rct.test.chksum != rct.file.chk256) {
  warning("Checksum is not equal to config")
}

## Yearwise Visualisations
```

```{r, message = FALSE}
#aea_data <- read_csv("../Data/trials_2023.csv") %>% 
#  janitor::clean_names()
```

```{r}
aea_data <- clean_names(aea_orig)
```


```{r}
current_year <- 2024
file_year <- 2023
```

## Data Wrangling

```{r}
aea_data_year <- aea_data %>% 
  mutate(first_registered_on = as.Date(first_registered_on, format = "%Y-%m-%d")) %>% 
  mutate(first_registered_on = str_replace(first_registered_on, "00", "20" )) %>% 
  mutate(first_registered_year = format(as.Date(first_registered_on), "%Y"))
```


```{r}
year_cnt <- aea_data_year %>% 
  group_by(first_registered_year) %>% 
  summarise(cnt = n()) %>% 
  ungroup()
```



# Creating data set with month and year

```{r}
aea_year_month <- aea_data_year %>% 
  mutate(
    first_month_year = format(as.Date(first_registered_on), "%Y-%m"),
    first_month = format(as.Date(first_registered_on), "%m")
  )
```

```{r}
# Creating variable to reflect month (used for cumulative count predictions)
aea_year_month <- aea_data_year %>% 
  mutate(
    first_month_year = format(as.Date(first_registered_on), "%m-%Y"),
    first_month = format(as.Date(first_registered_on), "%m")
  )
```

# Creating counts of registrations by year
```{r}
year_cnt <- aea_year_month %>% 
  group_by(first_registered_year) %>% 
  summarise(cnt_yr = n()) %>% 
  ungroup() 

#Data set of counts by year (excluding the current year)
year_wo_current <- year_cnt %>% 
  filter(first_registered_year != current_year)
```



```{r}
year_cnt
```

### Summary of code

In this section, the data has been loaded through the API, following which, the first registered year and month were extracted from the variable `first_registered_on`; these variables are called `first_registered_year` and `first_month`, respectively. After this, I created a dataset which summarizes the total number of registrations for each year. I also created a dataset with these counts, but without the observations for 2023 to facilitate the predictions below.

## Predictions for total counts

```{r}
cnt_lm <- lm(cnt_yr ~ as.numeric(first_registered_year), data = year_wo_current) 
summary(cnt_lm)
```

```{r}
# Creating data frame with prediction for current year
years <- data.frame(first_registered_year = c(current_year))

pred_cnt_current <- data.frame(year = c(current_year - 1, current_year), cnt = c(year_cnt$cnt_yr[year_cnt$first_registered_year == as.character(current_year - 1)], predict(cnt_lm, years)))
```


```{r}
min_year <- as.numeric(min(aea_data_year$first_registered_year))
outputs <- "../Output"

year_wo_current %>% 
  mutate(first_registered_year = as.numeric(first_registered_year)) %>% 
  ggplot(aes(x = first_registered_year, y = cnt_yr)) +
  geom_line(color = "olivedrab4") +
  geom_text(aes(label = cnt_yr), color = "olivedrab4", position = position_nudge(y = -2), vjust = -0.9) +
  geom_line(aes(x = year, y = cnt), data = pred_cnt_current, linetype = "dashed", color = "olivedrab4") +
  geom_point(aes(x = year, y = cnt), data = pred_cnt_current, color = "olivedrab4") +
  geom_point(color = "olivedrab4") +
  scale_x_continuous(
    name = "Year",
    limits = c(min_year, current_year), breaks = seq(min_year, current_year, 2))+
  scale_y_continuous(
    breaks = seq(0, 1500, 250)
  ) +
  labs(title = NULL, y = NULL) +
  theme(
    plot.title = element_blank(),
    axis.title.y = element_blank()
  )+
  theme_minimal()

ggsave(file.path(outputs, paste0("reg_pre_year_", file_year, ".pdf")),width=3.5,height=3.5,units="in")
ggsave(file.path(outputs, paste0("reg_pre_year_", file_year, ".png")),width=3.5,height=3.5,units="in")

num_regsyearly <- round(pred_cnt_current %>% filter(year == file_year) %>%
                                      pull(cnt),0)

 update_latexnums(paste0("regsyearly"), num_regsyearly)
```


### Summary of code

In this section, I created a linear regression model to predict the total number of registrations in 2023, based on the year. For this, I used the dataset with the registration counts for each year (excluding 2023). I did this since the data reflected records until November of 2023, which means that using the existing data would be an inaccurate reflection of the number of registrations in 2023. Finally, I graphed the existing data and the predictions, with the prediction indicated by a dashed line.


## Predictions for cumulative counts

```{r}
cnt_mnth_yr_current <- aea_year_month %>% 
  filter(first_registered_year == as.character(current_year)) %>% 
  group_by(first_month) %>% 
  summarise(cnt = n()) %>% 
  ungroup()
```

```{r}
yr_cnt_no_current <- filter(year_cnt, first_registered_year != as.character(current_year))

cum_cnt_no_current <- data.frame(
  cum_cnt = cumsum(yr_cnt_no_current[, 2])
  )

cum_cnt_no_current <- cbind(yr_cnt_no_current[, 1], cum_cnt_no_current) 
```

```{r}
years <- data.frame(first_registered_year = c(current_year))

cnt_current <- data.frame(
  "year" = c(current_year - 1, current_year),
  "cnt" = c(
    cum_cnt_no_current$cnt_yr[cum_cnt_no_current$first_registered_year == as.character(current_year-1)],
    ( predict(cnt_lm, years)+ cum_cnt_no_current$cnt_yr[cum_cnt_no_current$first_registered_year == as.character(current_year-1)])
  )
)
```


```{r}
cum_cnt_no_current %>% 
  mutate(first_registered_year = as.numeric(first_registered_year)) %>% 
  ggplot(mapping = aes(x = first_registered_year, y = cnt_yr)) +
  geom_line(color = "olivedrab4") +
  geom_point(color = "olivedrab4") +
  geom_line(
    data = cnt_current,
    mapping = aes(x = year, y = cnt),
    linetype = "dashed",
    color = "olivedrab4"
  ) +
  geom_point(
    data = cnt_current,
    mapping = aes(x = year, y = cnt),
    color = "olivedrab4"
  ) +
  geom_text(
    aes(x = first_registered_year, y = cnt_yr, label = cnt_yr),
    vjust = -0.9,
    color = "olivedrab4"
  ) +
  scale_x_continuous(
    limits = c(min_year, current_year), breaks = seq(min_year, current_year, 2))+
  labs(title = NULL, y = NULL, x = "Year") +
  theme(
    plot.title = element_blank(),
    axis.title.y = element_blank()
  ) +
  theme(legend.position = c(0.87, 0.25))+
  theme_minimal() 


num_regscumul <- round((cnt_current %>% filter(year == file_year) %>%
                                      pull(cnt))/100,0)*100

update_latexnums(paste0("regscumul"),num_regscumul)

ggsave(file.path(outputs,paste0("reg_cumulative_", file_year, ".pdf")),width=3.5,height=3.5,units="in")
ggsave(file.path(outputs,paste0("reg_cumulative_", file_year, ".png")),width=3.5,height=3.5,units="in")

```


## Predictions for pre vs post reg

```{r}
aea_data_year <- aea_data_year %>% 
  mutate(intervention_start_date = as.Date(intervention_start_date, format = "%Y-%m-%d")) %>% 
  mutate(intervention_start_date = str_replace(intervention_start_date, "00", "20" ))
```


```{r}
pre_reg_cnt <- aea_data_year %>% 
  mutate(pre_post = ifelse(first_registered_on < intervention_start_date, "pre_reg", "post_reg")) %>% 
  group_by(first_registered_year, pre_post) %>% 
  summarise(reg_cnt = n()) %>% 
  ungroup() 

pre_reg_no_current <- pre_reg_cnt %>% 
  filter(first_registered_year != as.character(current_year))
```


```{r}
pre_reg_lm <- lm(reg_cnt ~ as.numeric(first_registered_year) + pre_post, data = pre_reg_no_current)
summary(pre_reg_lm)
```

```{r}
years_reg <- data.frame(first_registered_year = c(current_year), pre_post = c("post_reg", "pre_reg"))

reg_pred_current <- data.frame(
  year = c(as.character(current_year-1), as.character(current_year-1), current_year, current_year), 
  pre_post = c("pre_reg", "post_reg"),
  cnt = c(
    pre_reg_cnt$reg_cnt[pre_reg_cnt$first_registered_year == as.character(current_year-1) & pre_reg_cnt$pre_post == "pre_reg"],
    pre_reg_cnt$reg_cnt[pre_reg_cnt$first_registered_year == as.character(current_year-1) & pre_reg_cnt$pre_post == "post_reg"],
    predict(pre_reg_lm, years_reg))
  )
```

```{r}
pre_reg_no_current$first_registered_year <- as.numeric(pre_reg_no_current$first_registered_year)

reg_pred_current$year <- as.numeric(reg_pred_current$year)

ggplot(data = pre_reg_no_current, mapping = aes(x = first_registered_year, y = reg_cnt, color = pre_post)) +
  geom_path(aes(group = pre_post)) +
  geom_point() +
  theme_minimal() +
  geom_path(aes(x = year, y = cnt, color = pre_post, group = pre_post), data = reg_pred_current, linetype = "dashed") +
  geom_point(aes(x = year, y = cnt, color = pre_post), data = reg_pred_current) +
  geom_text(
    data = filter(pre_reg_no_current, pre_post == "post_reg"),
    aes(x = first_registered_year, y = reg_cnt, label = reg_cnt), vjust = -1, hjust = 0.75,
    color = "olivedrab4"
  ) +
  geom_text(
    data = filter(pre_reg_no_current, pre_post == "pre_reg"),
    aes(x = first_registered_year, y = reg_cnt, label = reg_cnt), vjust = 1.5, hjust = 0.25,
    color = "maroon"
  ) +
  scale_color_manual(
    values = c("olivedrab4", "maroon")
  ) +
  labs(title = NULL, y = NULL, x = "Year") +
  theme(
    plot.title = element_blank(),
    axis.title.y = element_blank()
  ) +
  scale_x_continuous( limits = c(min_year, current_year), 
                      breaks = seq(min_year, current_year, 2))+
  theme_minimal()+
  theme(legend.position = c(0.87, 0.15))

ggsave(file.path(outputs, paste0("post_pre_reg_", file_year, ".pdf")),width=3.5,height=3.5,units="in")
ggsave(file.path(outputs, paste0("post_pre_reg_", file_year, ".png")),width=3.5,height=3.5,units="in")
```


## Predictions for pap vs total counts

```{r}
pap_cnt <- aea_data_year %>% 
  filter(analysis_plan_documents != "None") %>% 
  group_by(first_registered_year) %>% 
  summarise(pap_cnt = n()) %>% 
  cbind(year_cnt[, 2])

pap_wo_current <- pap_cnt %>% 
  filter(first_registered_year != current_year)
```

```{r}
pap_lm <- lm(pap_cnt ~ as.numeric(first_registered_year), data = pap_wo_current)
summary(pap_lm)
```


```{r}
pap_lm <- lm(pap_cnt ~ as.numeric(first_registered_year), data = pap_wo_current)
summary(pap_lm)
```


```{r}
pap_reg <- data.frame(first_registered_year = c(current_year))

pap_pred_current <- data.frame(
  year = c(current_year-1, current_year),
  pap_cnt = c(
    pap_cnt$pap_cnt[pap_cnt$first_registered_year == as.character(current_year-1)],
    predict(pap_lm, pap_reg)),
  cnt_yr = c(
    pap_cnt$cnt_yr[pap_cnt$first_registered_year == as.character(current_year-1)],
    predict(cnt_lm, pap_reg))
  )
```

```{r}
pap_wo_current %>% 
  mutate(first_registered_year = as.numeric(first_registered_year)) %>% 
  ggplot() +
  geom_line(aes(x = first_registered_year, y = pap_cnt, color = "PAP")) +
  geom_point(aes(x = first_registered_year, y = pap_cnt, color = "PAP")) +
  geom_line(
    data = pap_pred_current,
    mapping = aes(x = year, y = pap_cnt, color = "PAP"),
    linetype = "dashed"
  ) +
  geom_point(
    data = pap_pred_current,
    mapping = aes(x = year, y = pap_cnt, color = "PAP")
  ) +
  geom_line(aes(x = first_registered_year, y = cnt_yr, color = "Total")) +
  geom_point(aes(x = first_registered_year, y = cnt_yr, color = "Total")) +
  geom_line(
    data = pap_pred_current,
    mapping = aes(x = year, y = cnt_yr, color = "Total"),
    linetype = "dashed"
  ) +
  geom_point(
    data = pap_pred_current,
    mapping = aes(x = year, y = cnt_yr, color = "Total")
  ) +
  scale_color_manual(
    values = c("Total" = "maroon", "PAP" = "olivedrab4")
  ) +
  theme_minimal() +
  scale_x_continuous( limits = c(min_year, current_year), breaks = seq(min_year, current_year, 2))+
  scale_y_continuous(
    breaks = seq(0, 1500, 250)
  ) +
  scale_x_continuous(limits = c(min_year, current_year), breaks = seq(min_year, current_year, 2))+
  labs(title = NULL, y = NULL, x = "Year", color = "Total Registrations \nand PAP") +
  theme(
    plot.title = element_blank(),
    axis.title.y = element_blank()
  ) +
  geom_text(
    aes(x = first_registered_year, y = pap_cnt, label = pap_cnt),
    vjust = 1.5,
    color = "olivedrab4"
  ) +
  geom_text(
    aes(x = first_registered_year, y = cnt_yr, label = cnt_yr),
    vjust = -0.6,
    color = "maroon"
  ) +
  theme(legend.position = c(0.87, 0.15), legend.key.size = unit(0.25, 'cm'))
  

ggsave(file.path(outputs, paste0("pap_reg_", file_year, ".pdf")),width=3.5,height=3.5,units="in")
ggsave(file.path(outputs, paste0("pap_reg_", file_year, ".png")),width=3.5,height=3.5,units="in")
```



## Predictions for percentage PAP

```{r}
pap_wo_current <- pap_wo_current %>% 
  mutate(pap_percent = (pap_cnt / cnt_yr))

pap_pred_current <- pap_pred_current %>% 
  mutate(pap_percent = (pap_cnt / cnt_yr))
```


```{r}
pap_wo_current %>% 
  mutate(first_registered_year = as.numeric(first_registered_year)) %>%
  ggplot() + 
  geom_line(
    mapping = aes(x = first_registered_year, y = pap_percent),
    color = "olivedrab4"
  ) + 
  geom_point(
    mapping = aes(x = first_registered_year, y = pap_percent),
    color = "olivedrab4"
  ) +
  geom_line(
    data = pap_pred_current,
    mapping = aes(x = year, y = pap_percent),
    linetype = "dashed",
    color = "olivedrab4"
  ) +
  geom_point(
    data = pap_pred_current,
    mapping = aes(x = year, y = pap_percent),
    color = "olivedrab4"
  ) +
  geom_text(
    aes(x = first_registered_year, y = pap_percent, label = round(pap_percent * 100, 2)),
    vjust = -1.85,
    color = "olivedrab4"
  ) +
  labs(title = NULL, y = NULL, x = "Year") +
  theme(
    plot.title = element_blank(),
    axis.title.y = element_blank()
  ) +
  scale_y_continuous(
    labels = scales::percent,
    limits = c(0, 0.5)
  ) +
  theme_minimal()+
  scale_x_continuous(limits = c(min_year, current_year), 
                     breaks = seq(min_year, current_year, 2))
  

ggsave(file.path(outputs, paste0("pap_per_reg_", file_year, ".pdf")) ,width=3.5,height=3.5,units="in")
ggsave(file.path(outputs, paste0("pap_per_reg_", file_year, ".png")),width=3.5,height=3.5,units="in")
```


```{r}
#### Functions:
sep_help <- function(col, sep){
  max <- 0
  for (i in 1:length(col)){
    if (is.na(col[i])){
      next
    }
    iter <- str_count(col[i], sep)
    if (iter > max){
      max = iter
    }
    else{
      next
    }
  }
  return(max)
}

sep_ls <- function(col,sep,name){
  num <- sep_help(col,sep)
  num <- num + 1
  nums <- 1:num
  listy <-  paste(name, nums,sep = "")
  return(listy)
}
better_sep <- function(df,col,sep,name){
  names <- sep_ls(col,sep,name)
  str <-deparse(substitute(col))
  co <- sub(".*\\$", "",str)
  new_df <- df %>%
    separate(co, names, sep =sep)
  return(new_df)
}

reshape_long <- function(df, var_name){
  nms <- colnames(df)
  end1 <- str_detect(nms,var_name)
  end <- sum(end1 == TRUE)
  vn <- paste(var_name,"1",sep = "")
  pos <-match(vn, nms)
  pos_min <- pos-1
  nms <- nms[1:pos_min]
  nms <- c(nms, var_name)
  new_df <- data.frame(matrix(ncol= length(nms), nrow = 0))
  colnames(new_df) <- nms
  for (q in 1:nrow(df)){
    iter <- df[q,]
    bool <- sapply(df, is.na)[q,]
    x<-1
    e <- var_name
    for (i in x:end){
      y <- paste(e,i, sep = "")
      if (bool[y] == TRUE){
        break
      }
      else{
        x = x+1
      }
    }
    x = x-1
    df_dup <- iter[rep(seq_len(nrow(iter)), each = x), ]
    df_new <- data.frame(matrix(ncol= length(new_df), nrow = x))
    df_new[,1:pos_min] <- df_dup[,1:pos_min]
    colnames(df_new) <- nms
    j = pos
    for (k in 1:nrow(df_new)){
      res <- as.character(df_dup[k,j])
      df_new[k,pos] = res
      j = j+1
    }
    new_df <- rbind(new_df, df_new)
  }
  return(new_df)
}
```



```{r}
years <- c(min_year, 2015,2017, 2022, file_year)
cum_reg_users <- c(744,1778,3472,8255,12453)
# adjust the partial 2023 number
#avg = (cum_reg_users[5] - cum_reg_users[4])/(4*12+11)
#cum_reg_users <- c(cum_reg_users,cum_reg_users[length(cum_reg_users)]+avg)
df <- tibble(Year = years, Registered.users = cum_reg_users) %>%
  mutate(label = as.character(Registered.users))

registered.users.estimate = df %>% filter(Year==current_year) %>% pull(Registered.users)
print(registered.users.estimate)
registered.users.rounded = floor(registered.users.estimate/100)*100

#update_latexnums("registeredusers",registered.users.rounded)


b <- ggplot(data=df, aes(x=Year,y=Registered.users))+
  geom_line(data = df,
            aes(y = Registered.users, group = 1),
            color = "olivedrab4", linetype = 1, size=1.5) +
  geom_point(data = df,
            aes(y = Registered.users, group = 1),
            color = "olivedrab4") +
  ggtitle(" ") +
  geom_text(y= df$Registered.users,
            label= df$label, vjust = 1.4,hjust = -.05) +
  scale_y_continuous(expand=c(0.1, 0),
                     n.breaks = 8) +
   scale_x_continuous(limits = c(min_year, current_year+1), 
                     breaks = seq(min_year, current_year+1, 2))+
  labs(y= "", x= "Year") +
  theme(text = element_text(size = 20)) +
  theme_minimal()
b
ggsave(file.path(outputs,paste0("registered_users_",file_year,".pdf")), b,width=3.5,height=3.5,units="in")
ggsave(file.path(outputs,paste0("registered_users_",file_year,".png")), b,width=3.5,height=3.5,units="in")

```



```{r}
### Getting number of active users:
# Defined by # of PIs with active projects or on registrations that have been updated in the last year

## First getting the right subset
aea_sm <- select(aea_orig, c(Title, Last.update.date,End.date,Primary.Investigator,Other.Primary.Investigators))
#
 aea_sm$Last.update.date <- as.Date(aea_sm$Last.update.date, format = "%B %d, %Y")
 aea_sm$End.date <- as.Date(aea_sm$End.date)
#
 today <- Sys.Date()
#
 aea_sm <- filter(aea_sm, End.date >= today | Last.update.date >= paste0(file_year, "-02-01"))
#
#
# ### Then we separate out the PIs:
 Oth <- select(aea_sm, -c(Primary.Investigator))
#
 Oth <- better_sep(Oth,Oth$Other.Primary.Investigators,"; ","PIs")
 Oth_long <- reshape_long(Oth,"PIs")
#
 Prim <- aea_sm %>%
   dplyr::rename(PI = Primary.Investigator) %>%
   select(PI)
#
 Oth <- Oth_long %>%
   dplyr::rename(PI = PIs) %>%
   select(PI)
#
 fin <- rbind(Prim,Oth)
#
 fin$PI <- str_trim(fin$PI)
 fin <- filter(fin, PI != "")
#
 fin$PI <- gsub("\\s*\\([^\\)]+\\)","",as.character(fin$PI))
#
 fin$PI <- rm_email(fin$PI)
 fin$PI <- str_trim(fin$PI)
#
 fin$PI <- sub("^(\\S*\\s+\\S+).*", "\\1", fin$PI)
#
 fin$PI <- tolower(fin$PI)
 fin <- distinct(fin,PI)
 fin <- fin[order(fin$PI),]
#
 print(paste0("The number of active registered users is: ",length(fin)))
#
 num_activeusers <- length(fin)
# You cannot use a number or an underscore in the Latex variables
 update_latexnums(paste0("activeusers"),num_activeusers)


```







```{r}
source("99_write_nums.R",echo=TRUE)
```









